---
title: "Build Blog"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # Set WD to Root
here::i_am("_dev/build-blog.Rmd")
library(here)
library(blogdown)
```

## Ref:

Follow the steps from this tutorial:

-  [Youtube](https://www.youtube.com/watch?v=MrW5XFf7aps&t=1263)
-  [Github](https://github.com/ivelasq/2022-01-25_building-a-blog-with-r)   
-  [Real Test App](https://hugo-apero-docs.netlify.app)

## Create New Site

If you are not using RStudio, you can create a new empty directory, and call the new_site() function in the directory in the R console to create a new site project:

```{r}
# new_site(theme = "hugo-apero/hugo-apero", 
#            format = "toml",
#            sample = FALSE,
#            empty_dirs = TRUE)
```


## When not Sure

```{r}
blogdown::check_site()
```


## Live Preview Site

Addins -> blogdown -> Serve Site

```{r}
blogdown::serve_site()
```

## Build Site

```{r}
blogdown::build_site()
```


## Blog

### New Blog

```{r}
# blogdown::new_content("blog/test-blog")
```



## Config

### Overall Config

in `config.toml`


## Images

For all image files (favicon, logo, and sharing_image), the files should be placed in the /static/ folder in your project root. The default config.toml file shows them inside /static/img/, for example:

config.toml
static/
└── img/
    ├── favicon.ico 
    ├── blogophonic-mark-dark.png
    └── papillons.jpg
    
### Img Location
    
```{r}
# fs::dir_create(here("static/img"))
fs::dir_tree(here("static/img"))
```
    
    
    
    
    
